### 2017-03-10 ResearchNotes/stat_exps.tex
Adds new statistic

>>>>

\subsection{\texttt{STAT\_007} - Number of Students per Course and Number of
Approved Students per Course}

We plot what the title states. The grey bars show the number of students
overall. The blue bars show the number of approved students. Each bar is one
course. Figure~\ref{fig_stat_007} shows the results of this statistics.

    \includegraphics[width=\linewidth]{../src/stat_007_results/plot}

    \caption
        [Number of Students per Course and Number of Approved Students per
        Course]
        {Number of Students per Course and Number of Approved Students per
        Course.}

    \label{fig:stat_007}
\end{figure}
